Language-Based Security for Low-Level MPC

### 2024-07-18 ppdp24/example-gmw.tex
checkpoint

For example, the following program uses our GMW library to define
a circuit with a single \eand\ gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
         let s1 = encodegmw("s1",1,2) in
         let s2 = encodegmw("s2",2,1) in
         decodegmw(andgmw("z",s1,s2))
\end{verbatimtab}
By convention we will assume that all gates are assigned unique output
identifiers $\ttt{"z"}$, and that all programs are in the form
of a sequence of let-bindings followed by a call to $\decodegmw$
wrapping a circuit.

>>>>

For example, the following program uses our GMW library to define
a circuit with a single \eand\ gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
         let s1 = encodegmw("s1",2,1) in
         let s2 = encodegmw("s2",1,2) in
         decodegmw(andgmw("z",s1,s2))
\end{verbatimtab}
By convention we will assume that all gates are assigned unique output
identifiers, and that all programs are in the form
of a sequence of let-bindings followed by a call to $\decodegmw$
wrapping a circuit.

### 2024-07-18 ppdp24/gmw.tex
checkpoint

\begin{fpfig}[t]{2-Party GMW circuit library.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in]@2;
      m[in]
    }

@@

    xorgmw(z, x, y) { m[z]@1 := (x+y)@1; m[z]@2 := (x+y)@2; m[z] }

>>>>

\begin{fpfig}[t]{2-party GMW circuit library.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in]@i2;
      m[in]
    }

@@

    xorgmw(z, x, y)
    { m[z]@1 := (x xor y)@1; m[z]@2 := (x xor y)@2; m[z] }
